\TheTitle

### 2019-07-11 Paper1/introduction.tex
comment on kinetic flux
paper small corrections

Intrusive methods do not suffer from this problem, since the computation is directly carried out on the moments, i.e. their time evolution can be recorded during the computation. Also for steady problems, the fact that the moments are known in each iteration enables the computation of the stochastic residual, which indicates when to stop the iteration towards the steady state solution. However intrusive methods are in general more difficult to implement and come along with higher numerical costs. The main idea of these methods is to derive a system of equations for the moments and then implementing a numerical solver for this system: Testing the initial problem \eqref{eq:hyperbolicProblem} with $\varphi_i$ for $|i|\leq M$ yields

@@

@@

In this paper, we present a semi-intrusive code framework, which facilitates the task of implementing general intrusive methods. The framework only requires the numerical flux of the deterministic problem (as well as an entropy if IPM is used). We thereby provide the ability to recycle existing implementations of deterministic solvers.
Furthermore, we investigate intrusive methods for steady problems and compare them against collocation methods. The steady setting provides different opportunities to take advantage of features of intrusive methods: 
\begin{itemize}
\item Accelerate convergence to the IPM steady state solution by applying IPM as a post-processing step for collocation methods: We converge the moments of the solution to a steady state with an inaccurate, but cheap collocation method and then use the resulting collocation moments as starting values for an expensive but accurate intrusive method such as IPM, which we then again converge to steady state. 
\item Compute inexact dual variables \eqref{eq:dualProblem} for IPM: Since the moments during the iteration process are inaccurate, i.e. they are not the correct steady state solution, we propose to not fully converge the dual iteration, which computes \eqref{eq:dualProblem}. 
\end{itemize}
In addition to these two strategies for steady problems, we make use of adaptivity: The intrusive nature of SG and IPM can be used to locally increase the number of moments whenever the solution has a complex structure in the random variable (as well as decrease the number of moments if not). We test the effectiveness of these acceleration ideas by comparing results with stochastic-Collocation for the uncertain NACA test case.

>>>>

Intrusive methods do not suffer from this problem, since the computation is directly carried out on the moments, i.e. their time evolution can be recorded during the computation. Also for steady problems, the fact that the moments are known in each iteration enables the computation of the stochastic residual, which indicates when to stop the iteration towards the steady state solution. However, intrusive methods are in general more difficult to implement and come along with higher numerical costs. The main idea of these methods is to derive a system of equations for the moments and then implementing a numerical solver for this system: Testing the initial problem \eqref{eq:hyperbolicProblem} with $\varphi_i$ for $|i|\leq M$ yields

@@

\begin{align}\label{eq:SGClosure}

@@

In this paper, we present a semi-intrusive code framework, which facilitates the task of implementing general intrusive methods. The framework only requires the numerical flux of the deterministic problem (as well as an entropy if IPM is used). We thereby provide the ability to recycle existing implementations of deterministic solvers.
Furthermore, we investigate intrusive methods for steady problems and compare them against collocation methods. The steady setting provides different opportunities to take advantage of features of intrusive methods: 
\begin{itemize}
\item Accelerate convergence to the IPM steady state solution by applying IPM as a post-processing step for collocation methods: We converge the moments of the solution to a steady state with an inaccurate, but cheap collocation method and then use the resulting collocation moments as starting values for an expensive but accurate intrusive method such as IPM, which we then again converge to steady state. 
\item Compute inexact dual variables \eqref{eq:dualProblem} for IPM: Since the moments during the iteration process are inaccurate, i.e. they are not the correct steady state solution, we propose to not fully converge the dual iteration, which computes \eqref{eq:dualProblem}. 
\end{itemize}
In addition to these two strategies for steady problems, we make use of adaptivity: The intrusive nature of SG and IPM can be used to locally increase the number of moments whenever the solution has a complex structure in the random variable (as well as decrease the number of moments if not). We test the effectiveness of these acceleration ideas by comparing results with stochastic-Collocation for the uncertain NACA test case as well as a bent shock tube problem.

### 2019-07-11 Paper1/main.tex
Paper continued
vtk plot and paper continued
adaptivity section in paper started + multi D notation intro corrected
paper small corrections

\begin{abstract}
Methods for quantifying the effects of uncertainties in hyperbolic problems can be divided into intrusive and non-intrusive techniques. A main drawback of intrusive methods is the need to implement new code, whereas collocation methods recycle a given deterministic solver. Furthermore, intrusive methods come with increased computational costs, making it hard to compete with non-intrusive methods.
In this work, we present a code framework, which facilitates the implementation of intrusive methods by recycling parts of deterministic codes. Additionally, we introduce methods to decrease numerical costs of intrusive methods for steady problems. We demonstrate the effectiveness of the proposed strategies by comparing results of the uncertain NACA0012 testcase as well as the shallow water equations.
\end{abstract}

@@

\input{introduction}
\input{framework}
\input{colloc_ipm}
\input{one_shot_ipm}
\input{results}
\input{summary_outlook}

\bibliographystyle{unsrt}  
\bibliography{references}
\end{document}

>>>>

\begin{abstract}
Methods for quantifying the effects of uncertainties in hyperbolic problems can be divided into intrusive and non-intrusive techniques. A main drawback of intrusive methods is the need to implement new code, whereas collocation methods recycle a given deterministic solver. Furthermore, intrusive methods come with increased computational costs, making it hard to compete with non-intrusive methods.
In this work, we present a code framework, which facilitates the implementation of intrusive methods by recycling parts of deterministic codes. Additionally, we introduce methods to decrease numerical costs of intrusive methods for steady problems. We demonstrate the effectiveness of the proposed strategies by comparing results of the uncertain NACA0012 testcase as well as a bent shock tube experiment.
\end{abstract}

@@

\input{introduction}
\input{framework}
\section{Strategies for steady problems}
\input{colloc_ipm}
\input{one_shot_ipm}
\input{adaptivity}
\input{results}
\input{summary_outlook}

\newpage
\bibliographystyle{unsrt}  
\bibliography{references}
\end{document}
